An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-03-29 poly-embed-journal/poly-embed-journal.tex
Revisiting properties proofs

\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}

@@

\paragraph{Related works.}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
Moreover~\citet{zhang2020bayes} describes the impact of the hypothesis class has on consistency, and when consistency relative to the hypothesis class differs from Bayes consistency; the latter is what we describe in this paper when we say ``consistency.''

@@

    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
  (For intuition, one can consider the relative interiors in $\reals^n_+$, but we need to consider interiors in order to apply previous results.)
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
%  Moreover, consider the linear transformation $P: \ell \mapsto [\mathbb{I}_{n-1}, \vec 0] \risk{\ell}$ projecting $\risk{\ell}$ down to $n-1$ dimensions.
  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$. \jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead.}

@@

	Now consider $\Y'\subset \Y$, $\Y'\neq\emptyset$.
	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
	Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
	As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
\end{proof}

@@

From the more succinct embedding condition in Proposition~\ref{prop:embed-risk-poly}, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
For example, this can be seen by a loss that is polyhedral in the convex hull of $\phi(\R)$, but smooth outside that region.

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
 \begin{proof}
	The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
	Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
	Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$.
	Since $L$ is polyhedral and $\gamma(p)\cap \R$ is nonempty for all $p \in \simplex$, we have $\risk{L} = \risk{L|_{\R}}$ polyhedral by Lemma~\ref{lem:poly-loss-poly-risk}.
 \end{proof}

We now turn to the reverse direction: which discrete losses are embedded by some polyhedral loss?
Perhaps surprisingly, we show that \emph{every} discrete loss is embeddable,
using a construction via convex conjugate duality which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
Note however that the number of dimensions $d$ required could be as large as $|\Y|$, which is particularly undesirable in structured prediction and information retrieval problems with exponentially many outcomes.
Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the convex calibration and embedding dimensions.
%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}

@@

\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  we use the same trick as in the proof of Proposition~\ref{prop:embed-bayes-risks}.
Consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that reduces to an affine subspace.
Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined by $u \mapsto (-\ell)^*(u) \ones - u$ where $\ell$ is that same as it is in Proposition~\ref{prop:embed-bayes-risks}, so that $\inprod{\ell(r)}{p} = \inprod{\L(\varphi(r))}{p} = \inprod{L'(A(\varphi(r)))}{p} $ for all $p \in \simplex$.
The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro since we haven't made the change in proposition 1 yet.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Polyhedral losses: indirect elicitation implies consistency}\label{sec:embed-props}
%\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
%\raf{Please fix refs, maybe by removing the duplicates from the appendix}
\btw{JESSIE: Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}
\btw{JESSIE: Should this section be before or after embedding losses, since the results in this section are used in the proofs in the embedding losses section?  Narrative of having props then losses: here is this toolkit we have for understanding this notion of embedding, now here is how we apply it to the machine learning thing you actually care about.  Narrative of losses then props: BOOM here's this cool thing, and btw this is how we show it.  I think for a journal I'm inclined towards the latter, but that opinion is not very strong.}

@@

\jessiet{New to journal version}
\begin{lemma}\label{lem:embed-defs-equiv}
	%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function.
	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
	\raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
	Consider a loss $\ell : \R \to \reals_+^\Y$, defined so that $\ell : r \mapsto L(\varphi(r))$, i.e. $\ell = L|_{\varphi(\R)}$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
	Now, we claim that $L$ embeds $\ell$.
	%    To see this, consider that Condition (i.) of matching embedded loss values is met by construction of $\ell$.
	Using Proposition~\ref{prop:embed-bayes-risks}, showing $\risk{L} = \risk{\ell}$ suffices to show that $L$ embeds $\ell$.

	First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
	$(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
	Consider that if we did not have $(1) \geq (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$.
	Therefore the property it embeds, $\gamma$ is degenerate at $p$, i.e. $\gamma(p) = \emptyset$, yielding a contradiction.
	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell(r)}$ by construction of $\ell$.
	%
	%Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
	%We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
	%Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
	%Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.

@@

By Lemma~\ref{lem:embed-defs-equiv}, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
Moreover, we can assume that finite properties are non-redundant without much loss of generality.
\begin{definition}[Finite property, non-redundant]
	A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
	$\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
\end{definition}

@@

Before we state Proposition~\ref{prop:embed-trim}, which is needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).

@@

\btw{JESSIE: Again, figures/an example might help clarify this}
When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
\jessiet{This lemma new to journal version}
\begin{lemma}\label{lem:embedded-level-sets-trim}
	Let $\Gamma$ be an elicitable property.
	If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
\end{lemma}
\begin{proof}
	Let $L$ elicit $\Gamma$.
	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
	\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional. 
	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
	\raft{The main action is here.  (1) Epigraph of $-\risk{L}$. (2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet. (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $\risk{L}$, which is concave, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered in one of two cases:
	First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
	Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.

@@

\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	%\raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
	Let $L$ elicit $\Gamma$.

@@

	\raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?  (Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete. \jessie{Added in the conditions of Lemma 3 to be a bit more thorough.}}
	2 $\Rightarrow$ 1:
	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
	We have $\U \subset \reals^d$ and $\Gamma(p) \cap \U \neq \emptyset$ for all $p$, since we have $p \in \Gamma_{u_i}$ for some $u_i \in \U$.
	Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.

@@

	1 $\Rightarrow$ 3: 
	Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
	The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the simplex.
	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.
	%	\hrule
	%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
	%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
	%	As the risks are equal, this is also true for $\Gamma$.
	%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
	%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
	%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
	%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.

>>>>

\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\affhull}{\mathrm{affhull}}

@@

\paragraph{Related works.}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.
Moreover,~\citet{zhang2020bayes} describe the impact of the hypothesis class has on consistency, and when consistency relative to the hypothesis class differs from Bayes consistency; the latter is what we describe in this paper when we say ``consistency.''

@@

    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
  (For intuition, one can consider the relative interiors in $\reals^n_+$, but we need to consider interiors in order to apply previous results.)
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
%  Moreover, consider the linear transformation $P: \ell \mapsto [\mathbb{I}_{n-1}, \vec 0] \risk{\ell}$ projecting $\risk{\ell}$ down to $n-1$ dimensions.
  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$. \jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead.}

@@

	Now for $p \not \in \int{\simplex}$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
	Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
	As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
\end{proof}

@@

From the more succinct embedding condition in Proposition~\ref{prop:embed-risk-poly}, we can in turn simplify the condition that a loss embeds \emph{some} discrete loss: it does if and only if its Bayes risk is polyhedral.
(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
Note that the Bayes risk, a function from distributions over $\Y$ to the reals, may be polyhedral even if the loss itself is not.
For example, this can be seen by a loss that is polyhedral in the convex hull of $\varphi(\R)$, but smooth outside that region.

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
 \begin{proof}
 	\jessie{Lemma 4 is redundant with this proof, and we don't really need the proof.  We have $L$ polyhedral $\implies \risk{L}$ polyhedral (L4) $\iff$ $L$ embeds a discrete loss (P2).}
	The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
	Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
	Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$.
	Since $L$ is polyhedral and $\gamma(p)\cap \R$ is nonempty for all $p \in \simplex$, we have $\risk{L} = \risk{L|_{\R}}$ polyhedral by Lemma~\ref{lem:poly-loss-poly-risk}.
 \end{proof}

We now turn to the reverse direction: which discrete losses are embedded by some polyhedral loss?
Perhaps surprisingly, we show that \emph{every} discrete loss is embeddable,
using a construction via convex conjugate duality which has appeared several times in the literature (e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
Note however that the number of dimensions $d$ required could be as large as $O(|\Y|)$, which is particularly undesirable in structured prediction and information retrieval problems with exponentially many outcomes.
Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
%\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}

@@

\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  we use the same trick as in the proof of Proposition~\ref{prop:embed-bayes-risks}.
Consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that reduces to an affine subspace.
Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro for proofreading.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Polyhedral losses: indirect elicitation implies consistency}\label{sec:embed-props}
%\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
%\raf{Please fix refs, maybe by removing the duplicates from the appendix}

@@

\jessiet{New to journal version}
\begin{lemma}\label{lem:embed-defs-equiv}
	%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}.
	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
	\raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
	Consider a loss $\ell : \R \to \reals_+^\Y$, defined so that $\ell : r \mapsto L(\varphi(r))$, i.e. $\ell = L|_{\varphi(\R)}$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$.

	First, we show that for all $p \in \simplex$, we have $(1) \inf_{u \in \reals^d}\inprod{p}{L(u)} = (2) \inf_{r \in \R}\inprod{p}{L(\varphi(r))}$, and the equality of risks follows.
	$(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$ and definition of infimum. 
	Consider that if we had $(1) < (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$ \jessie{BUG: NEED THE INFIMUM TO BE ATTAINED}, and therefore, we would have $\gamma(p) = \emptyset$, yielding a contradiction. 
	This gives us $(1) = (2)$, so we have $\risk{L} = \risk{L|_{\varphi(\R)}} = \risk{\ell(r)}$ by construction of $\ell$.
	%
	%Now consider the property $\Gamma' := p \mapsto \Gamma(p) \cap \varphi(\R)$.
	%We have $\Gamma'$ nondegenerate since $\Gamma$ embedding $\gamma$ implies that, for all $p \in \simplex$, there is some $r \in \R$ such that $\varphi(r) \in \Gamma(p)$.
	%Therefore, for all $p \in \simplex$, we have $\inf_{r \in \R}\inprod{p}{L(\varphi(r))} = \inf_{r \in \R} \inprod{p}{\ell(r)}$, which yields $\risk{L|_{\varphi(\R)}} = \risk{\ell}$.
	%Chaining the two equalities, we now have $\risk{L} = \risk{\ell}$.

@@

By Lemma~\ref{lem:embed-defs-equiv}, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
Moreover, we can assume that finite properties are non-redundant without much loss of generality.
\begin{definition}[Finite property, non-redundant]
	\jessie{Feels like this should be earlier}
	A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
	$\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
\end{definition}

@@

Before we state Proposition~\ref{prop:embed-trim}, which is needed to prove many of the statements in \S~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).

@@

\btw{JESSIE: Again, figures/an example might help clarify this}
When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
\jessiet{This lemma new to journal version}
\begin{lemma}\label{lem:embedded-level-sets-trim}
	Let $\Gamma$ be an elicitable property.
	If $\Gamma$ embeds a (non-redundant) finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)\proposedadd{=\trim(\gamma)}$.
\end{lemma}
\begin{proof}
	Let $L$ elicit $\Gamma$.
	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
	%\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional in $\affhull(\simplex)$. 
	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
	\raft{The main action is here.  (1) Epigraph of $-\risk{L}$. (2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet. (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $-\risk{L}$, which is convex, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered as faces of the epigraph of $-\risk{L}$, and therefore a face of the induced power diagram.
	Therefore, we remove lower-dimensional faces, as they are proper subsets of the level sets of embedded reports, and conclude such $\Gamma_u \not \in \trim(\Gamma)$.
	% in one of two cases:
	%First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
	%Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.

@@

\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \affhull(\simplex)$.
	\end{enumerate}
	%\raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
	Let $L$ elicit $\Gamma$.

@@

	\raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?  (Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete. \jessie{Added in the conditions of Lemma 3 to be a bit more thorough.}}
	2 $\Rightarrow$ 1:
	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
	We have $\U \subset \reals^d$ and $\Gamma(p) \cap \U \neq \emptyset$ for all $p$, since we have $p \in \Gamma_{u_i}$ for some $u_i \in \U$.
	Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete and never empty.

@@

	1 $\Rightarrow$ 3: 
	Let $\varphi: \R \to \reals^d$ be the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
	The latter set is equal to $\{\gamma_r : r \in \R\}$ by Lemma~\ref{lem:embedded-level-sets-trim}.
	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the affine hull of the simplex.
	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.
	%	\hrule
	%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
	%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
	%	As the risks are equal, this is also true for $\Gamma$.
	%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
	%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
	%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
	%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.
